Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-05-06 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
add ref

Our last example of modified gravity theories are the so-called
EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
%
They are described by the action
%
\begin{equation} \label{eq:action_eft}
    S_{\rm EFT} = \frac{1}{16 \pi}
    \int \dd^4x \sqrt{-g}
    \left[ R
    +
    \sum_{n \geqslant 2} \ell_{\rm EFT}^{2n - 2}\, L^{(2n)}
    \right]\,,
\end{equation}
%
where $\ell_{\rm EFT}$ is a length-scale assumed to be small compared to the length-scale $M$
associated with a BH (i.e., $\ell_{\rm EFT} / M \ll 1$), and $L^{(2n)}$ are corrections
that introduce higher-order curvature tensors (with $2n$ metric derivatives).

>>>>

Our last example of modified gravity theories are the so-called
EFTs of GR~\cite{Endlich:2017tqa,Sennett:2019bpc,AccettulliHuber:2020dal,deRham:2020ejn,Cano:2020cao,Cano:2021myl}.
%
They are described by the action
%
\begin{equation} \label{eq:action_eft}
    S_{\rm EFT} = \frac{1}{16 \pi}
    \int \dd^4x \sqrt{-g}
    \left[ R
    +
    \sum_{n \geqslant 2} \ell_{\rm EFT}^{2n - 2}\, L^{(2n)}
    \right]\,,
\end{equation}
%
where $\ell_{\rm EFT}$ is a length-scale assumed to be small compared to the length-scale $M$
associated with a BH (i.e., $\ell_{\rm EFT} / M \ll 1$), and $L^{(2n)}$ are corrections
that introduce higher-order curvature tensors (with $2n$ metric derivatives).
